Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-03-21 defesa/article/article.tex
wip

%% The graphicx package provides the includegraphics command.
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{subcaption}
\journal{EJOR}

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newdefinition{rmk}{Remark}
\newdefinition{definition}{Definition}
\newproof{pf}{Proof}

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}

@@

		\begin{abstract}
			%% Text of abstract
			Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to place fixed shape ellipses on the plane to cover demand points
			maximizing a function depending on the value of covered points.
			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances having with up to seven hundred demand points and five ellipses.
		\end{abstract}

@@

@@

\section{Determining every location of an ellipse given its shape and three points}\label{section:e3p}

@@

\section{Implementation Details}\label{section:implementation}

\section{Numerical Experiments}\label{section:numerical}

\section*{References}
	%% New version of the num-names style
	\bibliographystyle{elsarticle-num}
	\bibliography{../references}

>>>>

%% The graphicx package provides the includegraphics command.
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{siunitx}
\sisetup{group-separator = {,}}

\usepackage{multirow}

\journal{EJOR}

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{prp}{Proposition}
\newtheorem{lem}{Lemma}
\newdefinition{rmk}{Remark}
\newdefinition{definition}{Definition}
%\newproof{pf}{Proof}
%\renewcommand\qedsymbol{$\blacksquare$}

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}

@@

		\begin{abstract}
			%% Text of abstract
			Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to place fixed shape ellipses on the plane to cover demand points
			maximizing a function depending on the value of covered points.
			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances with up to seven hundred demand points and five ellipses.
		\end{abstract}

@@

\section{Definition}\label{section:definition}
\input{definition.tex}

@@

\section{Determining every center and angle of rotation of an ellipse given its shape and three points that it must contain}\label{section:e3p}

@@

\section{Improvements}\label{section:improvements}
\input{improvements.tex}

%\section{Reducing the CLS size}\label{section:reducing_cls}
%\input{reducing_cls.tex}

%\section{Prunning the Backtracking Tree}\label{section:prunning}
%\input{prunning.tex}

\section{Implementation Details}\label{section:implementation}
\input{implementation.tex}

\section{Numerical Experiments}\label{section:numerical}
\input{numerical.tex}

\section{Conclusion}\label{section:conclusion}
\input{conclusion.tex}

\clearpage
\section*{References}
	%% New version of the num-names style
	\bibliographystyle{elsarticle-num}
	\bibliography{../references}

### 2020-03-21 defesa/article/definition.tex
wip

Additionally, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one ellipse, we omit the index referring to the facility, and we use $\partial$ as the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ denotes an ellipse with shape parameters $(a_1, b_1)$ centered at $q_1$.

>>>>

We define an equivalence and a partial order relation between solutions of both MCE and MCER as follows.
Two solutions $Q$ and $Q'$ of MCE (MCER), are said to be equivalent to each other if
they both cover the same set of demand points.
% $\cup_{j=1}^m \Pp \cap E_j(q_j) = \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($ \cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$). That is, two solutions are equivalent if they cover the same set of points.
We also define a partial order: $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.

%if, and only if $\cup_{j=1}^m \Pp \cap E_j(q_j) \subset \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($\Pp \cap\cup_{j=1}^m E_j(q_j, \theta_j) \subset \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$). That is, $Q' \succ Q$ if, and only if the set of points covered in solution $Q$ is a subset of the points covered in solution $Q'$.

%%% esse paragrafo ainda ta estranho.
Additionally, we denote by $\partial$ the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ represents the set of points $\{p \in \R^2\colon ||p-q_1||_{a_1,b_1,0} = 1\}$. Also, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one facility, we omit the index referring to the ellipse.

### 2020-03-21 defesa/article/mce.tex
wip

Similarly to the method developed in \cite{church:1984} for the Euclidean PMCLP, we will describe a Candidate List Set (CLS) of possible locations for each ellipse and then propose an algorithm that constructs solutions combining the possible locations in each ellipse's CLS.
Also, based on the approach of \cite{church:1984} for the Euclidean PMCLP, and in \cite{chazelle:1986} for the problem of covering points by one unit disk, we will construct the CLS for each ellipse by using a property of the one-facility MCE.
Although, it is intuitive that it is possible to adapt the ideas used for solving the problems involving Euclidean disks for axis-parallel ellipses, using the results of \cite{bi}, which studies the problem of determining the intersection of $n$ strictly convex disks with fixed radius, we will prove that for MCE, we have all the necessary geometric properties to develop an algorithm following those approaches.

We start by introducing a lemma stating that any solution of the one-facility MCE can be related to the intersection of coverage regions of ellipses centered at the points covered in that solution.

\begin{lem}\label{lema:mce-mwc}
	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$.
\end{lem}
\begin{proof}
	Let $u, v \in \R^2$, then we have that $u \in E(v)$ if, and only if $v \in E(u)$, which is proved simply by observing that:
	\begin{equation}\label{eq:peq}
	u \in E(v) \Leftrightarrow ||u-v||_{a, b, 0} \le 1 \Leftrightarrow v \in E(u).
	\end{equation}
	As $\Pp \cap E(q) = A$ can be written as: for all $p \in A$, $p \in E(q)$. Then, using \autoref{eq:peq}, we get that for all $p \in A$, $q \in E(p)$, which implies that $q \in \cap_{p\in A} E(p)$.
\end{proof}

%To define this equivalent problem, we need to first state an ellipse's property.
%Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE with one facility, and  $p, q \in \R^2$, we have that

%The equivalent problem is given by $n$ ellipses with shape parameters $(a, b)$ centered at $\Pp$. Let $q\in\R^2$ be a solution of MCE for one facility, by applying \autoref{eq:peq} to every point covered by $E(q)$, we obtain that
%\begin{equation}\label{eq:mce-mwc}
%\Pp \cap E(q) = \{p_i\in\Pp \colon q\in E(p_i)\},
%\end{equation}
%which implies that the problem of determining $q\in\R^2$ to maximize $w(\{p_i\in\Pp \colon q\in E(p_i)\})$, is equivalent to MCE for one facility. This changes the problem from determining a location for an ellipse given $n$ points to the problem of finding a point given $n$ ellipses with fixed locations.

%Let $A\subset \Pp$, from \autoref{eq:mce-mwc}, we have that if $\Pp \cap E(q) = A$ then $q \in \cap_{p\in A} E(p)$.

From , if we could identify every

Let $A \subset \Pp$, $|A|>1$, let us consider the intersection region $\cap_{p\in A} E(p) \neq \emptyset$. From \autoref{lema:mce-mwc}, we can also conclude that if $q \in \cap_{p\in A} E(p)$, then $A \subset \Pp \cap E(q)$.

In \cite{church:1984}, for the Euclidean PMCLP, it was proved that the border of this region contains at least one point that is an intersection between two fixed-radius circles with centers in $A$. This, as it turns out, is also true for ellipses, and a proof can be obtained from \cite{bi} where the problem of determining the intersection region of $n$ fixed-radius disks in a strictly convex normed plane is studied.
From that, we can conclude that there exists $u, v \in A$ and $q \in \partial E(u) \cap \partial E(v)$, such that $q \in \cap_{p\in A} E(p)$.
Before defining the CLS for each ellipse, we introduce a lemma stating two basic, and yet important properties about the intersection between two axis-parallel ellipses that have the same shape and distinct locations.

\begin{lem}\label{lema:e2p}
	Let $E$ be the coverage region of an axis-parallel ellipse with shape parameters $(a,b)$; and $v \in \R^2$, $v\neq0$. Then $|\partial E(0) \cap \partial E(v)| \le 2$, and $\partial E(0) \cap \partial E(v)$ can be determined analytically.
\end{lem}

\begin{proof}
	To determine the intersection points, consider the equality between the equations of $\partial E(0)$ and $\partial E(v)$:
	$x^2/a^2 + y^2/b^2 = (x-v_x)^2/a^2 + (y-v_y)^2/b^2.$
	This expression can be reduced to $y=\alpha x + \beta$, for some $\alpha, \beta$, which can then be plugged into $\partial E(0)$'s equation obtaining $x^2/a^2 + (\alpha x + \beta)^2/b^2 = 1$.
	We obtain the intersection points by solving this quadratic equation for $x$, and then, for each value of $x$,  determining $y$ from $y=\alpha x + \beta$.
\end{proof}
Next, we define the CLS of each ellipse, considering also the case where, in an optimal solution, an ellipse covers only one point.
\begin{definition}\label{def:cls_mce}
	Given an instance of MCE, for all $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
	\begin{equation}
	S_k = \Pp \cup \left(\bigcup_{1 \le i < j \le n} \partial E_k(p_i) \cap \partial E_k(p_j) \right).
	\end{equation}
\end{definition}

By \autoref{lema:e2p}, the CLS for each ellipse can be computed in $\bigO(n^2)$, and $|S_k| \le n + 2\binom{n}{2}$. Next, we establish a lemma stating that the set of solutions obtained by combining the possible locations in each ellipse's CLS contains at least one optimal solution.

\begin{thm}\label{thm:mce}
	Given an instance of MCE, and $S_1, \dots, S_m$ as defined by \autoref{def:cls_mce}, then the set $\Omega = \{(q_1, \dots, q_m) \colon \textnormal{ for all }q_k \in S_k \}$ contains an optimal solution of MCE and $|\Omega| \le n^{2m}$. 
\end{thm}
\begin{proof}
	Let $Q^*$ be an optimal solution of MCE for the given instance. Then, we are going to prove that there exists $Q' \in \Omega$, which is also optimal.

	For each $k=1, \dots, m$, let $X_k = \{p_i \in \Pp\colon p_i \in E_k(q_k^*)\}$.

@@

	If $|X_k| \le 1$, then there is at least one element in $S_k$ that makes $X_k \subset \Pp \cap E_k(q_k)$.

	If $|X_k| > 1$, then let $Y_k = \cap_{p \in X_k}E_k(p)$. By the results of \cite{bi}, we have that the boundary of $Y_k$ has vertices in the pairwise intersections of $\{\partial E_k(p) \colon p \in X_k\}$. Therefore, at least one vertex of $Y_k$ is in $S_k$, and any of those vertices produce a solution that covers at least the same points covered by $Q^*$.

	Lastly, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$. Hence, $|\Omega| \le n^{2m}$.
\end{proof}

With all this in hand, we define \autoref{algoritmo:mce}, which goes through every possible combination in the CLS of each ellipse. As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has $\bigO(mn^{2m+1})$ runtime complexity. 
In \autoref{section:numerical}, we give more details about the implementation of \autoref{algoritmo:mce} and analyze some numerical experiments for instances proposed in \cite{canbolat, andreta}, and for some new ones.

@@

		\item[]
		\Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
		\State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
		\EndProcedure
		\State
		\Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
		\If{$j = |\Rr|+1$}
		\State \Return $0$
		\EndIf

		\State $(q_j^*, \dots, q_m^*) \gets (0, \dots, 0)$
		\State Let $S_j$ be the CLS for the $j$-th ellipse as defined by \autoref{def:cls_mce}.
		%\State $S_j \gets \textnormal{CLS-MCE}(Z, a_j, b_j)$
		\For{$q_j \in S_j$}
		\State $Cov \gets \Pp \cap E_j(q_j)$
		\State $(q_{j+1}, \dots, q_m) \gets MCE_{bt}(Z \setminus Cov, \Ww, \Rr, j+1)\}$

>>>>

Similarly to the method developed in \cite{church:1984} for the Euclidean PMCLP, we will describe a Candidate List Set (CLS) of possible locations for each ellipse and then propose an algorithm that constructs solutions combining the possible locations in each ellipse's CLS.

To construct a CLS for each ellipse, based on the approach of \cite{church:1984} for the Euclidean PMCLP, and on \cite{chazelle:1986} for the problem of maximizing the coverage of points by a unit disk, we will describe some properties of the one-facility MCE, which will reduce our task to determining the pairwise intersection between ellipses centered at $\Pp$.

%Although, it is intuitive that it is possible to adapt the ideas used for solving the problems involving Euclidean disks for axis-parallel ellipses, using the results of \cite{bi}, which studies the problem of determining the intersection of $n$ strictly convex disks with fixed radius, we will prove that for MCE, we have all the necessary geometric properties to develop an algorithm following those approaches.

We start by introducing a proposition stating that any solution of the one-facility MCE can be related to the intersection of coverage regions of ellipses centered at the points covered in that solution.

\begin{prp}\label{lema:mce-mwc}
	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
\end{prp}
\begin{proof}
	Let $u, v \in \R^2$, then we have that $u \in E(v)$ if, and only if $v \in E(u)$, which is proved simply by observing that:
	\begin{equation}\label{eq:peq}
	u \in E(v) \Leftrightarrow ||u-v||_{a, b, 0} \le 1 \Leftrightarrow v \in E(u).
	\end{equation}
	Therefore, if $p\in A$, then by \autoref{eq:peq}, $q \in E(p)$, which implies $q \in \cap_{p\in A} E(p)$.
	The second part of the lemma also follows from \autoref{eq:peq} as if $q' \in \cap_{p\in A} E(p)$, then $||q' - p||_{a,b,0} \le 1$ for all $p \in A$.
\end{proof}

By \autoref{lema:mce-mwc}, we can ignore solutions that are not in $\cap_{p\in A} E(p)$, for some $A \subset \Pp$. Because ellipses can be described by strictly convex norms, we will show that the set $\cap_{p\in A} E(p)$ has some convenient properties, which can be used to narrow down the solutions' search space even more.

Let us assume that $|A|>1$ and consider the intersection region $\cap_{p\in A} E(p)$. 
In \cite{church:1984}, for the Euclidean PMCLP, it was proved that the border of this region contains at least one point that is an intersection between two fixed-radius circles with centers in $A$. For ellipses, this means that $ \cap_{p\in A} E(p)$ contains at least one element from the set $\cup_{u, v \in A}\partial E(u) \cap \partial E(v)$.

To prove that this is true, we resort to the results of \cite{bi}, which develops an algorithm to determine the intersection region of $n$ strictly convex disks of fixed radius. There, it is stated that this intersection region is bounded by the arcs of some of the disks that are part of the intersection, and also that the vertices of this region form a subset of the set of pairwise intersections of the $n$ given circles.
Following this result, we define the next lemma.

\begin{lem}\label{lema:mce}
	Let $q\in \R^2$ be a solution of MCE for the instance $(\Pp, \Ww, \{(a, b)\})$.
	If $|\Pp \cap E(q)|\ge 2$, then there exists $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, such that $q' \succ q$.
\end{lem}
\begin{proof}
	By \autoref{lema:e2p}, let $A=\Pp \cap E(q)$, we have that for any $q' \in \cap_{p\in A} E(p)$, $q' \succ q$. 
	Furthermore, by the results of \cite{bi}, we have that there exists $q' \in \cup_{u, v \in A}\partial E(u) \cap \partial E(v)$, such that $q' \in \cup_{p\in A} E(p)$. 
	Therefore, $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, and $q' \succ q$.
\end{proof}

Before defining the CLS for each ellipse, we introduce a proposition indicating how to compute the intersection between two axis-parallel ellipses.

\begin{prp}\label{lema:e2p}
	Let $E$ be the coverage region of an axis-parallel ellipse with shape parameters $(a,b)$; and $v \in \R^2$, $v\neq0$. Then $|\partial E(0) \cap \partial E(v)| \le 2$, and $\partial E(0) \cap \partial E(v)$ can be determined analytically.
\end{prp}

\begin{proof}
	To determine the intersection points, consider the equality between the equations of $\partial E(0)$ and $\partial E(v)$:
	$x^2/a^2 + y^2/b^2 = (x-v_x)^2/a^2 + (y-v_y)^2/b^2.$
	This expression can be reduced to $y=\alpha x + \beta$, for some $\alpha, \beta$, which can then be plugged into $\partial E(0)$'s equation obtaining $x^2/a^2 + (\alpha x + \beta)^2/b^2 = 1$.
	We obtain the intersection points by solving this quadratic equation for $x$, and then, for each value of $x$,  determining $y$ from $y=\alpha x + \beta$.
\end{proof}
Next, we define the CLS for each facility, taking into account solutions where the two points are contained on the ellipse as given by \autoref{lema:mce}, and also, solutions where the ellipse covers only one demand point.

\begin{definition}\label{def:cls_mce}
	Given an instance of MCE, for all $k \in \{1, \dots, m\}$, we define the CLS for the $k$-th ellipse as
	\begin{equation}
	S_k = \Pp \cup \left(\bigcup_{1 \le i < j \le n} \partial E_k(p_i) \cap \partial E_k(p_j) \right).
	\end{equation}
\end{definition}

By \autoref{lema:e2p}, the CLS for each ellipse can be computed in $\bigO(n^2)$, and $|S_k| \le n + 2\binom{n}{2}$. Next, we establish the main result of this section, which states that the set of solutions obtained by combining the possible locations in each ellipse's CLS contains at least one optimal solution.

\begin{thm}\label{thm:mce}
	Given an instance of MCE, and $S_1, \dots, S_m$ as defined by \autoref{def:cls_mce}, then the set $\Omega = \{(q_1, \dots, q_m) \colon \textnormal{ for all }q_k \in S_k \}$ contains an optimal solution of MCE and $|\Omega| \le n^{2m}$. 
\end{thm}
\begin{proof}
	Let $Q^*$ be a solution of MCE. Then, we are going to prove that there exists $Q' \in \Omega$, such that $Q'\succ Q^*$.

	For each $k\in \{1, \dots, m\}$, let $X_k = \{p_i \in \Pp\colon p_i \in E_k(q_k^*)\}$.

@@

	If $|X_k| \le 1$, then there is at least one element $q_k'\in S_k$ that makes $X_k \subset E_k(q_k')$.

	If $|X_k| > 1$, by \autoref{lema:mce}, we have that there exists $q_k' \in S_k$, such that $X_k \subset E_k(q_k')$.

	Lastly, by \autoref{lema:e2p}, we have that $|S_k| \le 2\binom{n}{2} + n = n(n+1)/2 \le n^2$. Hence, $|\Omega| \le n^{2m}$.
\end{proof}

With all this in hand, we define \autoref{algoritmo:mce}, which goes through every possible combination in the CLS of each ellipse. As evaluating each solution can be done in $\bigO(nm)$, we have that \autoref{algoritmo:mce} has $\bigO(mn^{2m+1})$ runtime complexity. 
In \autoref{section:improvements}, we give some suggestions of improvements that can be applied to the implementation of \autoref{algoritmo:mce}, and in \autoref{section:numerical}, we analyze the results obtained by \autoref{algoritmo:mce} for some numerical experiments.

@@

		\item[]
		\Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
		\State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
		\EndProcedure

		\item[]

		\Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
		\State $(q_j^*, \dots, q_m^*) \gets (0, \dots, 0)$
		\State Let $S_j$ be the CLS for the $j$-th ellipse as defined by \autoref{def:cls_mce}.
		%\State $S_j \gets \textnormal{CLS-MCE}(Z, a_j, b_j)$
		\For{$q_j \in S_j$}
			\State $Cov \gets \Pp \cap E_j(q_j)$
			\If{$j < |\Rr|$}
				\State $(q_{j+1}, \dots, q_m) \gets MCE_{bt}(Z \setminus Cov, \Ww, \Rr, j+1)\}$
			\EndIf

### 2020-03-21 defesa/article/mcer.tex
wip

\begin{definition}
	Two solutions $Q$ and $Q'$ of MCER, are said to be equivalent to each other if \mbox{$\Pp \cap \cup_{j=1}^m E_j(q_j, \theta_j) = \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$}. Also, if $\Pp \cap\cup_{j=1}^m E_j(q_j, \theta_j) \subset \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$, then we say that $Q' \succ Q$.
\end{definition}

Next, we introduce a lemma which states that any optimal solution of MCER has an equivalent solution where every ellipse that covers at least two points has two points on its border.

\begin{lem}\label{lema:mce_2b}
	Let $Q^*$ be a solution of MCER for an instance $(\Pp, \Ww, \{(a,b)\})$.
	If $|\Pp \cap E(q^*, \theta^*)| \ge 2$, then there exists a solution $Q$ for the same instance, such that $Q \succ Q^*$, and $|\Pp \cap \partial E(q, \theta)|\ge 2$.
\end{lem}

\begin{proof}
	First, let $\theta=\theta^*$ and ignore the angle of rotation as it does not change, and assume that we are dealing with an axis-parallel ellipse.

	Let $A=\Pp \cap E(q^*, \theta^*)$ and $X=\cap_{p \in A}E(p, \theta^*)$ be the region of intersection of ellipses centered at each point in $A$. By \cite{bi}, the vertices of $\partial X$ are in the set of pairwise intersections of $\{\partial E(p, \theta^*)\colon p \in A\}$. Setting $q$ as any of these vertices makes $E(q, \theta)$ have two points on its border.	
\end{proof}

%Next, we define, for an optimal solution, a set of equivalent solutions, such that any ellipse covering more than one point contains at least two points.

%\begin{definition}
%	Let $Q^*$ be an optimal solution of MCER. We define $\Pi(Q^*)$ as the set of every equivalent solution to $Q^*$, such that for any $Q \in\Pi(Q^*)$, for $j\in\{1, \dots, m\}$ with $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$, we have $|\Pp \cap \partial E_j(q_j', \theta_j')| \ge 2$.
%\end{definition}

Next, we introduce a notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains both points.

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=.22]{figures/feasible-angle2}
	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
	\label{fig:feasible-angle}
\end{figure}

For any $x\in\R^2$, we denote by $\angle x\in [0, \pi)$ the minimal angle between $x$ and the vector $(1, 0)$. Then, if $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as it is the angle that makes the ellipse's major-axis be parallel to the line that passes through $u$ and $v$.

@@

\begin{proof}
	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that $Q' \succ Q^*$ exists, and $\{u, v\} \subset \partial E(q', \theta^*)$. Therefore, $\theta^*\in\Phi(u,v)$.

@@

		\ForAll{$(q_j, \theta_j) \in S_j$}
		%\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$

		\If{$j < m$}
		\State $(q_{j+1},\theta_{j+1}); \dots; (q_m,\theta_m) \gets  MCER_{bt}(Z\setminus Cov, \Ww, \Rr, j+1)$
		\EndIf

>>>>

%To make the text more clear, we introduce an equivalence relation for the set of solutions of MCER, and also a order relation making the set of solutions partially ordered.

Let $(\Pp, \Ww, \{(a,b)\})$ be an instance of MCER, then given a solution $Q$ for it, with $|\Pp \cap E(q, \theta)| \ge 2$, if we rotate the coordinate system by $-\theta$, and use the result given by \autoref{lema:mce} for an axis-parallel ellipse, we can conclude that another solution $Q'$ exists, such that $Q' \succ Q$ and $|\Pp \cap \partial E(q', \theta)| \ge 2$. That is, given a solution for the one-facility MCER, we can obtain another one that covers the same points (possibly more) and the ellipse contains two demand points.

Next, we define a new notation that helps us characterize angles which given an ellipse rotated by it and two points, it is possible to find a center for the ellipse, such that it contains both points.

@@

%%%%% TODO: TERMINEI DE REVISAR AKI.

\begin{figure}[H]
	\centering
	\includegraphics[scale=.22]{figures/feasible-angle2}
	\caption{The solid border ellipses are rotated by a $(E, u,v)$-feasible angle, while the ellipse with a dashed border is rotated by a not $(E, u, v)$-feasible angle.}
	\label{fig:feasible-angle}
\end{figure}

For any $x\in\R^2$, we denote by $\angle x\in [0, \pi)$ the minimal angle between $x$ and the vector $(1, 0)$. If $\Phi(u,v)\neq\emptyset$, then $\angle(u-v)\in  \Phi(u,v)$ as $\angle(u-v)$ is the angle that makes the ellipse's major-axis, the longest segment crossing an ellipse, be parallel to the line that passes through $u$ and $v$.

@@

\begin{proof}
	According to \autoref{lema:mce}, there exists $\{u, v\} \subset \Pp \cap E(q^*, \theta^*)$, such that $Q' \succ Q^*$ exists, and $\{u, v\} \subset \partial E(q', \theta^*)$. Therefore, $\theta^*\in\Phi(u,v)$.

@@

		\ForAll{$(q_j, \theta_j) \in S_j$}
		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$

		\If{$j < |\Rr|$}
		\State $(q_{j+1},\theta_{j+1}); \dots; (q_m,\theta_m) \gets  MCER_{bt}(Z\setminus Cov, \Ww, \Rr, j+1)$
		\EndIf
